Feature Selection and Classification of \\ Spam on Social Networking Sites

### 2012-05-09 docs/paper/paper.tex
update

Social networks of any significant size witness a constant flow of spam, scams and phishing attacks. 
The nature of this unwanted activity, which we henceforth refer to collectively as ``spam" can be 
quite diverse, specific to a site's target audience and often not easily detectable. Marketers 
spam members with unwanted advertisements, fraudsters lure users with advance fee frauds and 
other confidence tricks, while others may attempt to steal user information by directing users 
to external phishing pages.

Sites with global reach see communication among its members in a number foreign languages with 
varying levels of ability. This means that much benign content shares characteristics including 
misspellings, awkward phrases, etc. that might have made certain types of common frauds and spam 
more easy to distinguish on US-based (or English-language) sites. Likewise, simple regional IP-based 
filtering to target high-spam countries like Nigeria and Ghana would prevent legitimate users 
located on these networks from accessing the site.

@@

\subsection{Spam Email \& Web}

>>>>

Social networking sites (SNSs) of any significant size witness a constant flow of spam, 
scams and phishing attacks.  The nature of this unwanted activity, which we henceforth refer to 
collectively as ``spam" can be 
quite diverse, specific to a site's target audience and often not easily detectable. Marketers 
spam members with unwanted advertisements, fraudsters lure users with advance fee frauds and 
other confidence tricks, while others may attempt to steal user information by directing users 
to external phishing pages.

Sites with global reach see communication among members in a variety foreign languages with 
varying levels of ability. This means that much benign content shares characteristics including 
misspellings, awkward phrases, and so on, that might have made certain types of common frauds and spam 
more easy to distinguish on US-based (or English-language) sites. Likewise, simple regional IP-based 
filtering to target high-spam countries like Nigeria and Ghana would prevent legitimate users 
located on blocked networks from accessing the site.

@@

\subsection{Email \& Web Spam}
